upwell_IDX

### 2020-05-14 upwell_IDX.Rmd
housekeeping
climatology

site_list_sub <- site_list_sub[c(-2, -3, -5, -6, -7,-9, -12, -13, -14),] # Here I keep all the sites with temperature obtained up to
# 2017 -kommetjie and Yzerfontein was removed as temperatures started in 1990s. 
# I took up till 2017 because the G1SST data starts frm 2010-present. To create a long time series to run through the heatwaveR algorithm, this was needed.
# save(site_list_sub, file = "Data_coast_angle/site_list_sub.Rdata")

@@

# Detect event: 
detect_event_custom <- function(df){
  res <- detect_event(df, threshClim2 = df$exceedance, minDuration = 1, coldSpells = T)
  return(res)
}
# Calculate the upwelling event metrics
SACTN_upwell_base <- SACTN_US %>% 
  dplyr::rename(t = date) %>% 
  group_by(site) %>% 
  nest() %>% 
  mutate(clim = purrr::map(data, ts2clm, pctile = 25, climatologyPeriod = c("1993-01-01", "2005-10-19"))) %>%
  select(-data) %>% 
  unnest(cols = clim) %>%
  left_join(SACTN_upwell, by = c("site", "t")) %>%
  filter(!is.na(exceedance)) %>%
  group_by(site) %>% 
  nest() %>% 
  mutate(exceed = purrr::map(data, detect_event_custom)) %>% 
  select(-data)

>>>>

site_list_sub <- site_list_sub[c(-2, -3, -5, -6, -7,-9, -12, -13, -14),] # Here I keep all the sites with temperature obtained up to
# 2017 -kommetjie and Yzerfontein was removed as temperatures started in 1990s. 
# I took up till 2017 because the SACTN data ends here.. To create a long time series to run through the heatwaveR algorithm, this was needed.
# save(site_list_sub, file = "Data_coast_angle/site_list_sub.Rdata")

@@

# Detect event: 
detect_event_custom <- function(df){
  res <- detect_event(df, threshClim2 = df$exceedance, minDuration = 1, coldSpells = T)
  return(res)
}
# Calculate the upwelling event metrics
SACTN_upwell_base <- SACTN_US %>% 
  dplyr::rename(t = date) %>% 
  group_by(site) %>% 
  nest() %>% 
  mutate(clim = purrr::map(data, ts2clm, pctile = 25, climatologyPeriod = c("1993-01-01", "2005-10-19"))) %>%
  dplyr::select(-data) %>% 
  unnest(cols = clim) %>%
  left_join(SACTN_upwell, by = c("site", "t")) %>%
  filter(!is.na(exceedance)) %>%
  group_by(site) %>% 
  nest() %>% 
  dplyr::mutate(exceed = purrr::map(data, detect_event_custom)) %>% 
  dplyr::select(-data)
